---
output:
  github_document:
    html_preview: true
always_allow_html: yes
editor_options: 
  chunk_output_type: console
---



<!-- README.Rmd generates README.md. -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  # collapse = TRUE,
  fig.align = "center",
  comment = "#>",
  fig.path = "man/figures/",
  message = FALSE,
  warning = FALSE
)
# options(width = 400)
```


# `{knapplyr}`

<!-- badges: start -->
[![Lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![GitHub last commit](https://img.shields.io/github/last-commit/knapply/knapplyr.svg)](https://github.com/knapply/knapplyr/commits/master)
[![Codecov test coverage](https://codecov.io/gh/knapply/knapplyr/branch/master/graph/badge.svg)](https://codecov.io/gh/knapply/knapplyr?branch=master)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/knapply/knapplyr?branch=master&svg=true)](https://ci.appveyor.com/project/knapply/knapplyr)
[![Travis-CI Build Status](https://travis-ci.org/knapply/knapplyr.svg?branch=master)](https://travis-ci.org/knapply/knapplyr)
[![License: GPL v3](https://img.shields.io/badge/License-GPLv3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0)
[![Depends](https://img.shields.io/badge/Depends-GNU_R>=3.1-blue.svg)](https://www.r-project.org/)
[![GitHub code size in bytes](https://img.shields.io/github/languages/code-size/knapply/knapplyr.svg)](https://github.com/knapply/knapplyr)
[![HitCount](http://hits.dwyl.io/knapply/knapplyr.svg)](http://hits.dwyl.io/knapply/knapplyr)
<!-- badges: end -->



 Utility functions to facilitate robust R programming that are _heavily_-inspired by `{purrr}`.
 
 `{knapplyr}` is meant to serve as a controlled environment for development and testing. The functions are not so much intended to be imported elsewhere, but instead to make it easy to have sane, tested, dependency-free utilities that can be easily used as internal, utility functions in other packages. Just add `/R/knapply-utils.R` to your package's `/R` folder and the functions will be accessible.

Considering the intent is that these functions are only used internally in packages, there are no exported functions. With that in mind, this following examples use `:::`.

```{r, echo=FALSE}
`%||%` <- knapplyr:::`%||%`
`%{NULL}%` <- knapplyr:::`%{NULL}%`
`%{}%` <- knapplyr:::`%{}%`
`%{NA}%` <- knapplyr:::`%{NA}%`
`%{""}%` <- knapplyr:::`%{""}%`
```

# Default-ers

```{r}
NULL %||% "common default replacement for `NULL`"
NULL %{NULL}% "default replacement for `NULL` following curly convention"
character(0) %{}% "default empty replacement"
NA %{NA}% "default NA replacement"
"" %{""}% "default empty string replacement"
```

```{r, echo=FALSE}
library(dplyr)
foos <- c("`%||%`",
          "`%{NULL}%`",
          "`%{}%`",
          "`%{NA}%`",
          '`%{""}%`')

exs <- c('NULL %||% "common default NULL replacement"',
         'NULL %{NULL}% "alternate NULL replacement"',
         'character(0) %{}% "default empty replacement"',
         'NA %{NA}% "default NA replacement"',
         '"" %{""}% "default empty string replacement"')

tibble(`{knapply} Function` = foos, Example = exs) %>% 
  mutate(Result = glue::glue("`{purrr::map_chr(Example, ~ eval(parse(text = .x)))}`"),
         Example = glue::glue('`{Example}`')) %>% 
  knitr::kable(format = "html", escape = FALSE)
```



## `.map*()`-ers

```{r, echo=FALSE}
.map <- knapplyr:::.map
.map_chr <- knapplyr:::.map_chr
.map_lgl <- knapplyr:::.map_lgl
.map_int <- knapplyr:::.map_int
.map_dbl <- knapplyr:::.map_dbl
```

```{r}
l1 <- list(a = 1:3, b = -1:-3)
l1
.map(l1, as.character)
.map_chr(l1, paste, collapse = ", ")
.map_int(l1, sum)
.map_dbl(l1, function(x) sum(x) * 2.5)
.map_lgl(l1, function(x) all(x > 0))
```

## `.map2*()`-ers

```{r, echo=FALSE}
.map2 <- knapplyr:::.map2
.map2_chr <- knapplyr:::.map2_chr
.map2_lgl <- knapplyr:::.map2_lgl
.map2_int <- knapplyr:::.map2_int
.map2_dbl <- knapplyr:::.map2_dbl
```

```{r}
l2 <- list(a = 4:6, b = -4:-6)
l2
.map2(l1, l2, c)
.map2_chr(l1, l2, paste, collapse = " | ")
.map2_int(l1, l2, min)
.map2_dbl(l1, l2, function(x, y) sort(c(x, y))[[1L]])
.map2_lgl(l1, l2, function(x, y) all(c(x, y) > 0))
```


```{r, echo=FALSE}
.set_names <- knapplyr:::.set_names
```

```{r}
n <- .set_names("named")
n
```




